Measuring causal influence with\\ back-to-back regression

### 2019-05-22 paper/meg_exps.tex
Sync

We attempt to identify which factors of $X$ explain the MEG
recordings $Y$ at each time sample and for each subject separately. To this aim,
we compare three methods (forward, backward and back-to-back
regressions). Corresponding results can be found in Figure \ref{fig:meg_twocurves}.

@@

Forward regression performs a regularized least-squares regression $A \in \mathbb{R}^{d_x \times d_y}$ from $X$ to $Y$, and estimates the causal influence $E_{i,i}$ as $\| A_{i, :} \|^2$.
%
Backward regression performs a regularized least-squares regression $B \in \mathbb{R}^{d_y \times d_x}$ from $Y$ to $X$, and estimates the causal influence $E_{i, i}$ as the Pearson correlation between the $i$-th column of $X$ and the $i$-th column of $YB$, using a validation sample.
%

@@

\paragraph{Back-to-back regression} We adapted back-to-back regression with two
changes. First, to avoid getting a slightly positively-biased estimate of the
factors contributing to the MEG signal, we swap the Tikhonov regularization of
the first regression $G$ with a truncated regularization. Truncation was fitted
 by maximum likelihood estimate, as implemented in scikit-learn principal
 component analysis. Second, to minimize the variance increase induced by
 bagging, we computed the inverse regularized covariance matrices outside
 bagging:
\begin{equation}
  G = (Y^T Y+\lambda_Y I)^{-1} Y_{train}^T X_{train}
\end{equation}
\begin{equation}
\hat X_{test} = Y_{test} \cdot G^T
\end{equation} where $\left(train,test\right)$ are partitions of the data.

@@

We show all the feature coefficients as a function of time in the stacked plots,
Figure \ref{fig:megresult}. Our method confirms previous findings in
neuroscience literature. In particular, \cite{kutas2011thirty} find that word
frequency correlates with a brain wave around 400ms. Similarly,
\cite{pegado2014timing} show that letter strings correlate with early brain
responses. Both these phenomena can be observed in Figures
\label{fig:meg_twocurves} and \ref{fig:megresult}, where we show that our
method is able to separate them more clearly than the forward regression
approach.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_result.pdf}
  \caption{We plot the coefficients corresponding to each of the features,
  describing their importance over time after stimuli onsets. We can observe that visual features start peaking around 150ms, while lexical features peak around 400ms. We show a similar plot for the Ridge regression baseline (forward) in Figure \ref{fig:ridgebaselineresult}.}
  \label{fig:megresult}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/ridgecv_baseline_result.pdf}
  \caption{Ridge regression baseline. All the coefficients appear to be
  linearly correlated, unlike our method in Figure \ref{fig:megresult}.}
  \label{fig:ridgebaselineresult}
\end{figure}

>>>>

We attempt to identify which factors of $X$ explain the MEG
recordings $Y$ at each time sample and for each subject separately. To this aim,
we compare three methods: forward regression, backward regression, and back-to-back regression.
Corresponding results can be found in Figure \ref{fig:meg_twocurves}.

@@

Forward regression performs a regularized least-squares regression $A \in \mathbb{R}^{d_x \times d_y}$ from $X$ to $Y$, and estimates the causal influence $E_{i,i}$ as $\| A_{i, :} \|^2$.
%
Backward regression performs a regularized least-squares regression $B \in \mathbb{R}^{d_y \times d_x}$ from $Y$ to $X$, and estimates the causal influence $E_{i, i}$ as the Pearson correlation between the $i$-th column of $X$ and the $i$-th column of $YB$, using a validation sample.
%
For back-to-back regression, we observed that two modifications improved its performance on MEG data.
%
First, we replace the Tikhonov regularization in the first regression by truncated SVD (performed as a maximum likelihood estimation of principal components).
%
Second, we invert the data covariances using all the data, and use these common inverses across B2BR repetitions.

@@

% \paragraph{Back-to-back regression} We adapted back-to-back regression with two
% changes. First, to avoid getting a slightly positively-biased estimate of the
% factors contributing to the MEG signal, we swap the Tikhonov regularization of
% the first regression $G$ with a truncated regularization. Truncation was fitted
%  by maximum likelihood estimate, as implemented in scikit-learn principal
%  component analysis. Second, to minimize the variance increase induced by
%  bagging, we computed the inverse regularized covariance matrices outside
%  bagging:
% \begin{equation}
%   G = (Y^T Y+\lambda_Y I)^{-1} Y_{train}^T X_{train}
% \end{equation}
% \begin{equation}
% \hat X_{test} = Y_{test} \cdot G^T
% \end{equation} where $\left(train,test\right)$ are partitions of the data.

@@

We aimed to estimate

We show these coefficients as a function of time in the stacked plots, in Figure
\ref{fig:megresult}.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_result.pdf}
  \caption{Average magnetosensor response across words for one subject.}
  \label{fig:megresult}
\end{figure}

### 2019-05-22 paper/paper.tex
Sync

\section{Related works}
\subsection{Back-to-back regression as a special case of canonical component analysis}
Formula (1) shows that back-to-back regression may be related to canonical component analysis (CCA).
%
In CCA, we are given two matrices X and Y (or size N,p and N,q) that describe different features measured on the same data sample, and characterize their proximity (that is, between the subspaces spanned by their columns) as the correlation between linear combinations of X and Y.

>>>>

\section{Related work}
Formula (1) shows that back-to-back regression may be related to canonical component analysis (CCA).
%
In CCA, we are given two matrices X and Y (or size N,p and N,q) that describe different features measured on the same data sample, and characterize their proximity (that is, between the subspaces spanned by their columns) as the correlation between linear combinations of X and Y.
